Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-02-05 paper/gloaguenNmfTraffic.tex
minor improvements

In this paper, several techniques based on non-negative factorization framework are studied in this application scenario on a simulated sound scene corpus. The task being to the best of our knowledge never been considered in the literature, we propose an experimental protocol to validate the studied approaches that complies with standard reproducible research recommendations. The results shows the interest of our proposed approach for a such sound environment as it improves the estimation of the road traffic sound level with a lowest error compared to basic methods.

@@

The main issue in the detection or recognition tasks is the overlap of environmental sounds. Although near major roads, traffic is predominant, there are many places where it overlaps with other sound sources which contribute significantly to the overall sound levels. To circumvent this issue, Socoro et al. propose to suppress time frames where there is significant overlap by considering an Anomalous Noise Events Detector \cite{socoro_anomalous_2017}. It consists in detecting the unwanted sound sources from labeled recordings, \textit{i.e.} that are not related to the traffic component. Those time frames are then discarded in order not to take them into account during the estimation of the traffic sound level. 
An alternative approach that we will follow in this paper is to consider the blind source separation paradigm to reliably estimate the traffic noise level, see Figure \ref{fig:diagram}. It consists in separating the contribution of the traffic from the other sources within a polyphonic scene. One major advantage of following such approach is that the estimate is continuously available, making the approach applicable in a wide range of urban areas, even where the traffic noise is relatively low compared to the remaining contributions.\\

@@

where $\mathbf{W} \in \mathbb{R}^+_{F \times K}$ is the \textit{dictionary} (or basis) matrix composed of audio spectra and $\mathbf{H} \in \mathbb{R}^+_{K \times N}$ is the \textit{activation} matrix which summarizes the temporal evolution of each element of $\mathbf{W}$. An illustrative example can be found in Figure  \ref{fig:example_NMF}.

@@

Algorithms have been proposed to solve the minimization problem (\ref{eq:min-D-WH}) iteratively such as the multiplicative update \cite{lee_algorithms_2000}, the alternating least square method \cite{cichocki_regularized_2007} or the projected gradient \cite{lin_projected_2007}. Here, the multiplicative update is chosen as it ensures convergence as proven in \cite{fevotte_algorithms_2011}.

@@

The supervised approach is useful when prior knowldge can be assumed for all the sources in the mixture, which is not a reasonable assumption in our application scenario. To some extend, prior knowledge can be considered for the traffic but not for the numerous kind of interferences that can occur in a realistic scenario. To better take into account the diverse nature of urban scenes, semi-supervised NMF (Sem-NMF)\cite{lee_semi-supervised_2010} is a good candidate as it offers more flexibility. This method assumes a \textit{dictionary} with a fixed part $\mathbf{W_s} \in \mathbb{R}^+_{F\times K}$, composed in our case of road traffic spectra, and with a mobile part, $\mathbf{W_r} \in \mathbb{R}^+_{F\times J}$ with $J <<K$, that is updated during optimization. In the literature, $J$ is set to a small number with respect to $K$ so as to force the optimization to still consider the fixed part of the dictionary %\cite{fevotte ?}
. The aim is to include in $\mathbf{W_r}$ the elements that are not related with the traffic. The problem (\ref{eq:nmf}) becomes

@@

We therefore propose an alternative scheme based on the unsupervised NMF. Usually in unsupervised, $\mathbf{W}$, as  $\mathbf{H}$, are initialized randomly. Here, as the concerned sound source is known and audio samples of car passages are available, an initial dictionary, $\mathbf{W_0}$, is learnt by converting the audio files in the spectra domain; see part \ref{part:dictionary_learning}. Then NMF is performed where $\mathbf{W}$ (eq. \ref{eq:updateW_unsup}) and $\mathbf{H}$ (eq.  \ref{eq:updateH_Sup}) are updated alternatively. $\mathbf{W}$ is therefore updated by forcing its initiation with \textit{a priori} knowledge but allowing it to adapt to the actual content of the scene under study,

@@

$D_{\theta}\left(\mathbf{W_0}_k \vert \vert \mathbf{W}_k \right) = 1$ means that the elements are identical (the $k$-th element of $\mathbf{W}$ is then considered as traffic element) whereas $D_{\theta}\left(\mathbf{W_0}_k \vert \vert \mathbf{W}_k \right)$ = 0 means that the elements are completely different. This measure is bounded between 1 and 0 and is an invariant with respect to scale. The $k$ value of $D_{\theta}\left(\mathbf{W_0} \vert \vert \mathbf{W} \right)$ are next sorted in descending order. The elements in $\mathbf{W}$ that can belong to $\mathbf{W}_{traffic}$ are selected by a \textit{hard thresholding} method. It is defined as:

@@

An illustrative example is shown in Figure \ref{fig:W_TI_NMF}.\\

@@

This database is divided into two categories: $i)$ the \textit{event} category, which are the brief sounds (from 1 to 20 seconds) that are considered as salient including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, whistling bird, sweeping broom, car horn, passing car, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, metallic noise, train, tramway, truck and voice}) and $ii)$ the \textit{background} or \textit{texture} category that includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. 154 sound samples that belong to this category are divided in 9 sound classes (\textit{whistling bird, construction site noise, crowd noise, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). These sounds are in .wav format sampled at 44.1 kHz. The sound class \textit{car passages} comes from 60 recordings of 2 cars (Renault Megane and Renault Scenic) made on the Ifsttar's runway at different speeds with multiple gear ratio. The other audio files have been found online (\textit{freesound.org}) and within the \textit{UrbanSound8k} database \cite{salamon_dataset_nodate}. Each sound class is composed of multiples samples (\textit{bird01.wav}, \textit{bird02.wav} \dots) to allow some diversity in the resulting mixture.
The software allows the user to control some high level parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may bring some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\

@@

This database allows us to create a wide diversity of realistic urban sound scenes from the road traffic point of view \cite{gloaguen_creation_2017}. A sound mixing corpus is composed of 6 sub-corpus of 25 audio files each lasting 30 seconds. Each sub-corpus is characterized by a specific generic sound class that summed with traffic will make the estimation of the traffic level more difficult. The classes are: \textit{alert} (car horn, siren), \textit{animals} (barking dog , whistling bird), \textit{climate} (wind, rain), \textit{humans} (crowd noise and voice), \textit{mechanics} (metallic and construction site noises) and \textit{transportation} (train, tramway and plane). In each file, traffic component is present as the sum of the background and event traffic sounds and is mixed with the other sound classes. The sound classes that are not related to the traffic component are summed up as the \textit{interfering} sound class. To test different scenarios, each audio file is duplicated with the traffic sound level of the entire sound scene, $L_{p,traffic}$, fixed to a specific level according to the sound level of the \textit{interfering} class, $L_{p,interfering}$,  following the relation (\ref{eq:tir}).

@@

with the \textit{Traffic Interference Ratio} $TIR \in$ [-12 -6 0 6  12] dB. When $TIR < 0$ dB, the traffic component is then less present than the interfering class. In the opposite, for $TIR > 0$ dB, the traffic class is louder than the interfering class. The total number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 $TIR$ values). The corpora are available for download at: \url{https://zenodo.org/record/1145855#.Wl2oPnkiGos}

@@

In order to prevent potential overfitting issues, the dictionary is built from a separate sound database dedicated specifically to this task. It is composed of 53 audio files of passing cars. These recordings have been made on the Ifsttar's runway too, with the same experimental conditions that the recordings of the \textit{SimScene} database but with two different cars (Dacia Sandero and Renault Clio). First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 50 $\%$ overlap, $nfft$). Then time/frequency windows of $F \times w_t $ dimensions are applied without overlapping on the spectrogram in order to consider several spectra for each audio file where $w_t \in [0.5~1]$ second. In each window, the root mean square value is calculated on each frequency bin to reduce the windowed spectrogram in one spectrum a of $F \times 1$ dimension. With this size of window, it is possible to obtain the characteristic pitches of the different audio samples. One obtain for each value of $w_t$, from the 53 audio samples of passing cars respectively 2218 and 1109 elements. Since the number of elements given by this processing is high, in order to reduce the computational time and avoid redundant information, a $K$-means clustering is applied to reduce the number of spectra to $K \in \left[ 25, 50, 100, 200\right]$. The $K$ centroids are then the elements of the dictionary. A special case is added where the root mean square of \textit{all} the spectrogram is applied ($w_t$ = $all$) in order to build a dictionary with the spectral envelope of each audio sample. In this case, 53 spectra are obtained. The $K$-means clustering algorithm is then reduced to $K \in \left[25 50 \right]$.

@@

The obtained dictionary is expressed with third octave bands and each basis vector of $\mathbf{W}$ is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ the $\ell$-1 norm. Table \ref{tab:experimental_factorsNMF} summarizes the experimental factors ($K$ and $w_t$) for the dictionary building and their related modalities. This last step allows us to reduce the dimensionality while preserving a rich description of the spectral content. Experimental validation consistently showed that considering octave bands do not impact the performance for the two estimators studied in this paper.

@@

Sup-NMF and Sem-NMF updates are computed for 400 iterations, which is sufficient to reach convergence. TI-NMF is performed on a lower number of iterations (60) to prevent $\mathbf{W}$ to not deviate too much from the initial dictionary.
%\ml{ca c'est pas genial, il aurait mieux vallu utiliser un coefficient de pondération pour que W n'avance pas trop vite...}

The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed with third octave bands ($F$ = 29). This coarser method allows the reduction of the matrix size and decreases the computation time. But,  must of all, by expressing the frequency axis on a log frequency axis,  the low frequencies, where the traffic energy is focused, are described more finely than the high frequencies. For TI-NMF, the threshold $t$ is set between 0.30 and 0.70 with a step of 0.01. Tables  \ref{tab:experimental_factorsFilter} and \ref{tab:experimental_factorsNMF} summarize the experimental factors and their related modalities.

@@

After having performed NMF on one scene, the average traffic sound level, $\tilde{L}_{p,traffic}$, of the entire scene is calculated,

@@

where $p_{rms}$ is the effective pressure deducted from $\left[\mathbf{WH} \right]_{traffic}$ and $p_0$ is the reference sound pressure, $p_0 = 2 \times 10^{-5} Pa$.  For each set of unique modalities of experimental factors, $M$ values of $\tilde{L}_{p,traffic}$, corresponding to the $M$ scenes, are then obtained.

@@

Compared with the filter errors, the choice of some NMF approaches makes it possible to decrease the error of the road traffic sound level estimation. The supervised approach is the only method that has an average error superior to the 500 Hz filter baseline. Sem-NMF and TI-NMF have better results. The lowest average error is obtained for TI-NMF, 2.19 $\pm$ 2.18, for $\beta$ = 1 and threshold $t$ = 0.42 with the dictionary factors $K$ = 200 and $w_t$ = 500 ms. On the other hand, the semi-supervised approach has a higher error but with a lower standard deviation (2.32 $\pm$ 1.26).

@@

However, the relatively high degree of freedom of Sem-NMF are restrictive for high $TIR$ as the errors exceed 2 dB for all sub-classes and increase with $TIR$ = 6 dB and 12 dB. In order to reduce $D(\mathbf{V} \vert \vert \mathbf{WH}$), without constraint, Sem-NMF is free to include traffic components in $\mathbf{W_r}$. Consequently, this behavior decreases the quality of the reconstruction of the traffic component. In Figure \ref{fig:Y_alert_12} for $TIR=12$ dB, the high frequency components of car horns have disappeared for the benefit of low frequency content. Consequently, the traffic sound level estimation is then underestimated as in Figure \ref{fig:lp_alert_12}. \\

@@

Finally, TI-NMF with a threshold $t = 0.42$ and $\beta$ = 1, offers the lowest average error (Table \ref{tab:results}). Unlike Sup-NMF, where $\mathbf{W}$ is fixed, and Sem-NMF, where only $\mathbf{W_r}$ is updated, TI-NMF updates $\mathbf{W}$ entirely to adjust prior knowledge to the scene under evaluation so as to adapt to the different sound environments. The closest elements of the traffic component defined in $\mathbf{W_0}$ are then extracted to deduce the traffic signal. In Figure \ref{fig:dist_-12_12}, the similarity $D_{\theta}(\mathbf{W_0}||\mathbf{W})$ is displayed for 3 sub-classes and $TIR$ = [-12, 12] dB.

@@

For high $TIR$, as the traffic is the main sound source, the similarity of the initial dictionary and $\mathbf{W}$ is higher what allows retaining more elements as traffic components and then decreases the error (< 1 dB). The kept elements are then more suited to the scenes than a fixed dictionary. The error for these $TIR$ is then due to the thresholding which put aside some elements that are nevertheless related to the traffic component. With a low threshold, it is possible to decrease the error. For $TIR$ = 12 dB, the average error on all the sub-classes is 0.22 ($\pm$ 0.08) dB with $t$ = 0.30. In opposite for $TIR$ = -12 dB, it is better to choose a high threshold $t$ = 0.55, the error decrease to 4.46 $\pm$ 1.66. In order to generalize this method and having no prior knowledge on the urban environment, the chosen threshold $t$ is then fixed to $t$ = 0.42 and is the one that best balanced these opposite cases.

>>>>

In this paper, several techniques based on non-negative factorization framework are studied in this application scenario on a simulated sound scene corpus. The task being to the best of our knowledge never been considered in the literature, we propose an experimental protocol to validate the studied approaches that complies with standard reproducible research recommendations. The results show the interest of our proposed approach for such sound environments as it improves the estimation of the road traffic sound level compared to basic methods.

@@

The main issue in the detection or recognition tasks is the overlap of environmental sounds. Although near major roads, traffic is predominant, there are many places where it overlaps with other sound sources which contribute significantly to the overall sound levels. To circumvent this issue, Socor\'o et al. propose to suppress time frames where there is significant overlap by considering an Anomalous Noise Events Detector \cite{socoro_anomalous_2017}. It consists in detecting the unwanted sound sources from labeled recordings, \textit{i.e.} that are not related to the traffic component. Those time frames are then discarded in order not to take them into account during the estimation of the traffic sound level. 
An alternative approach that we will follow in this paper is to consider the blind source separation paradigm to reliably estimate the traffic noise level, see Figure \ref{fig:diagram}. It consists in separating the contribution of the traffic from the other sources within a polyphonic scene. One major advantage of following such approach is that the estimate is continuously available, making the approach applicable in a wide range of urban areas, even where the traffic noise is relatively low compared to the remaining contributions.\\

@@

where $\mathbf{W} \in \mathbb{R}^+_{F \times K}$ is the \textit{dictionary} (or basis) matrix composed of audio spectra and $\mathbf{H} \in \mathbb{R}^+_{K \times N}$ is the \textit{activation} matrix which summarizes the temporal evolution of each element of $\mathbf{W}$. As the constraint of non-negativity of $\mathbf{W}$ and $\mathbf{H}$ is considered, NMF allows only additive combinations between the element of $\mathbf{W}$. It is then a part-based representation that NMF provides. An illustrative example can be found in Figure \ref{fig:example_NMF}.

@@

Algorithms have been proposed to solve the minimization problem (\ref{eq:min-D-WH}) iteratively such as the multiplicative update \cite{lee_algorithms_2000}, the alternating least square method \cite{cichocki_regularized_2007} or the projected gradient \cite{lin_projected_2007}. Here, the multiplicative update is chosen as it has been well studied in the literature and it ensures convergence of the results \cite{fevotte_algorithms_2011}.

@@

The supervised approach is useful when prior knowldge can be assumed for all the sources in the mixture, which is not a reasonable assumption in our application scenario. To some extend, prior knowledge can be considered for the traffic but not for the numerous kind of interferences that can occur in a realistic scenario. To better take into account the diverse nature of urban scenes, semi-supervised NMF (Sem-NMF)\cite{lee_semi-supervised_2010} is a good candidate as it offers more flexibility. This method assumes a \textit{dictionary} with a fixed part $\mathbf{W_s} \in \mathbb{R}^+_{F\times K}$, composed in our case of road traffic spectra, and with a mobile part, $\mathbf{W_r} \in \mathbb{R}^+_{F\times J}$ with $J <<K$, that is updated during optimization. In the literature, $J$ is set to a small number with respect to $K$ so as to force the optimization to still consider the fixed part of the dictionary \cite{lefevre2012semi}. The aim is to include in $\mathbf{W_r}$ the elements that are not related with the traffic. The problem (\ref{eq:nmf}) becomes

@@

We therefore propose an alternative scheme based on the unsupervised NMF. Usually in unsupervised, $\mathbf{W}$, as  $\mathbf{H}$, is initialized randomly. Here, as the concerned sound source is known and audio samples of car passages are available, an initial dictionary, $\mathbf{W_0}$, is learnt by converting the audio files in the spectra domain; see part \ref{part:dictionary_learning}. Then NMF is performed where $\mathbf{W}$ (eq. \ref{eq:updateW_unsup}) and $\mathbf{H}$ (eq.  \ref{eq:updateH_Sup}) are updated alternatively. $\mathbf{W}$ is therefore updated by forcing its initiation with \textit{a priori} knowledge but allowing it to adapt to the actual content of the scene under study,

@@

$D_{\theta}\left(\mathbf{W_0}_k \vert \vert \mathbf{W}_k \right) = 1$ means that the $k$-th element of $\mathbf{W}$ is identical to the $k$-th element of $\mathbf{W_0}$. In the opposite, $D_{\theta}\left(\mathbf{W_0}_k \vert \vert \mathbf{W}_k \right)$ = 0 means that the elements are completely different. This measure is bounded between 1 and 0 and is an invariant with respect to scale. The $k$ value of $D_{\theta}\left(\mathbf{W_0} \vert \vert \mathbf{W} \right)$ are next sorted in descending order. The elements in $\mathbf{W}$ that can belong to $\mathbf{W}_{traffic}$ are selected by a \textit{hard thresholding} method. It is defined as:

@@

An illustrative example is displayed in Figure \ref{fig:W_TI_NMF}.\\

@@

This database is divided into two categories: $i)$ the \textit{event} category, which are the brief sounds (from 1 to 20 seconds) that are considered as salient including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, whistling bird, sweeping broom, car horn, passing car, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, metallic noise, train, tramway, truck and voice}) and $ii)$ the \textit{background} or \textit{texture} category that includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. 154 sound samples that belong to this category are divided in 9 sound classes (\textit{whistling bird, construction site noise, crowd noise, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). These sounds are in .wav format sampled at 44.1 kHz. The sound class \textit{car passages} comes from 60 recordings of 2 cars (Renault Megane and Renault Scenic) made on the Ifsttar's runway at different speeds with multiple gear ratio. The other audio files have been found online (\textit{freesound.org}) and within the \textit{UrbanSound8k} database \cite{salamon_dataset_nodate}. Each sound class is composed of multiples samples (\textit{bird01.wav}, \textit{bird02.wav} \dots) to allow some diversity in the resulting mixture, see Figure \ref{fig:example_simScene}. The software allows the user to control some high level parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may bring some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\

@@

This database allows us to create a wide diversity of realistic urban sound scenes from the road traffic point of view \cite{gloaguen_creation_2017}. A sound mixing corpus is composed of 6 sub-corpus of 25 audio files each lasting 30 seconds. Each sub-corpus is characterized by a specific generic sound class that summed with traffic will make the estimation of the traffic level more difficult. The classes are: \textit{alert} (car horn, siren), \textit{animals} (barking dog , whistling bird), \textit{climate} (wind, rain), \textit{humans} (crowd noise and voice), \textit{mechanics} (metallic and construction site noises) and \textit{transportation} (train, tramway and plane). In each file, traffic component is present as the sum of the background and event traffic sounds while the \textit{interfering} sound class is the sound sources not related to it. To test different scenarios, each audio file is duplicated with the traffic sound level of the entire sound scene, $L_{p,traffic}$, fixed to a specific level according to the sound level of the interfering class, $L_{p,interfering}$,  following the relation (\ref{eq:tir}).

@@

with the \textit{Traffic Interference Ratio} $TIR \in$ [-12 -6 0 6  12] dB. When $TIR < 0$ dB, the traffic component is less present than the interfering class. In the opposite, for $TIR > 0$ dB, the traffic class is louder than the interfering class. The total number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 $TIR$ values). The corpora are available for download at: \url{https://zenodo.org/record/1145855#.Wl2oPnkiGos}

@@

In order to prevent potential overfitting issues, the dictionary is built from a separate sound database dedicated specifically to this task. It is composed of 53 audio files of passing cars. These recordings have been made on the Ifsttar's runway too, with the same experimental conditions that the recordings of the \textit{SimScene} database but with two different cars (Dacia Sandero and Renault Clio). First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 50 $\%$ overlap, $nfft$). Then time/frequency windows of $F \times w_t $ dimensions are applied without overlapping on the spectrogram in order to consider several spectra for each audio file where $w_t \in [0.5~1]$ second. In each window, the root mean square value is calculated on each frequency bin to reduce the windowed spectrogram in one spectrum a of $F \times 1$ dimension. With this size of window, it is possible to obtain the characteristic pitches of the different audio samples. One obtain for each value of $w_t$, from the 53 audio samples of passing cars respectively 2218 and 1109 elements. Since the number of elements given by this processing is high, in order to reduce the computational time and avoid redundant information, a $K$-means clustering algorithm is applied to reduce the number of spectra to $K \in \left[ 25,~50,~100,~200\right]$. The $K$ centroids are then the elements considered in the dictionary. A special case is added where the root mean square of \textit{all} the spectrogram is applied ($w_t$ = $all$) in order to build a dictionary with the spectral envelope of each audio sample. In this case, 53 spectra are obtained. The $K$-means clustering algorithm is then reduced to $K \in \left[25~50 \right]$.

@@

The obtained dictionary is expressed with third octave bands and each basis vector of $\mathbf{W}$ is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ the $\ell$-1 norm. Table \ref{tab:experimental_factorsNMF} summarizes the experimental factors ($K$ and $w_t$) for the dictionary building and their related modalities. This last step allows us to reduce the dimensionality while preserving a rich description of the spectral content. Experimental validation consistently showed that considering octave bands do not impact the performance of the estimator studied in this paper.

@@

Sup-NMF and Sem-NMF updates are computed for 400 iterations, which is sufficient to reach convergence. TI-NMF is performed on a lower number of iterations (60) to prevent $\mathbf{W}$ to not deviate too much from the initial dictionary.
The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed with third octave bands ($F$ = 29). This coarser method allows the reduction of the matrix size and decreases the computation time. But,  must of all, by expressing the frequency axis on a log frequency axis,  the low frequencies, where the traffic energy is focused, are described more finely than the high frequencies. For TI-NMF, the threshold $t$ is set between 0.30 and 0.70 with a step of 0.01. Tables  \ref{tab:experimental_factorsFilter} and \ref{tab:experimental_factorsNMF} summarize the experimental factors and their related modalities.

@@

For each setting, the estimator (frequency low-pass filter or NMF) is performed on the $M$ scenes of a sub-class. For one sound scene, the average traffic sound level, $\tilde{L}_{p,traffic}$, of the entire scene is calculated,

@@

where $p_{rms}$ is the effective pressure deducted from the remaining spectrogram ($\mathbf{V}_{f_c}$ or $\left[\mathbf{WH} \right]_{traffic}$) and $p_0$ is the reference sound pressure, $p_0 = 2 \times 10^{-5} Pa$.  For each set of unique modalities of experimental factors, $M$ values of $\tilde{L}_{p,traffic}$, corresponding to the $M$ scenes, are then obtained.

@@

Compared with the filter errors, the choice of some NMF approaches makes it possible to decrease the error of the road traffic sound level estimation. The supervised approach is the only method that has an average error superior to the 500 Hz filter baseline. Sem-NMF and TI-NMF have better results. The lowest average error is obtained for TI-NMF, 2.19 $\pm$ 2.18, for $\beta$ = 1 and threshold $t$ = 0.42 with the dictionary factors $K$ = 200 and $w_t$ = 500 ms. On the other hand, the semi-supervised approach has a higher error but a lower standard deviation (2.32 $\pm$ 1.26).

@@

However, the relatively high degrees of freedom of Sem-NMF are restrictive for high $TIR$ as the errors exceed 2 dB for all sub-classes and increase with $TIR$ = 6 dB and 12 dB. In order to reduce $D(\mathbf{V} \vert \vert \mathbf{WH}$), without constraint, Sem-NMF is free to include traffic components in $\mathbf{W_r}$. Consequently, this behavior decreases the quality of the reconstruction of the traffic component. In Figure \ref{fig:Y_alert_12} for $TIR=12$ dB, the high frequency components of the alert sounds are lower for the benefit of low frequency content. Consequently, the traffic sound level estimation is then underestimated as in Figure \ref{fig:lp_alert_12}. \\

@@

Finally, TI-NMF with a threshold $t = 0.42$ and $\beta$ = 1, offers the lowest average error (Table \ref{tab:results}). Unlike Sup-NMF, where $\mathbf{W}$ is fixed, and Sem-NMF, where only $\mathbf{W_r}$ is updated, TI-NMF updates $\mathbf{W}$ entirely to adjust prior knowledge to the scene under evaluation so as to adapt to the different sound environments. The closest elements of the traffic component defined in $\mathbf{W_0}$ are then extracted to deduce the traffic signal. In Figure \ref{fig:dist_-12_12}, the similarity $D_{\theta}(\mathbf{W_0}||\mathbf{W})$ is displayed for 3 sub-classes and $TIR \in $ [-12, 12] dB.

@@

For high $TIR$, as the traffic is the main sound source, the similarity of the initial dictionary and $\mathbf{W}$ is higher which allows retaining more elements as traffic components and then decreases the error (< 1 dB). The kept elements are then more suited to the scenes than a fixed dictionary. The error for these $TIR$ is then due to the thresholding which put aside some elements that are nevertheless related to the traffic component. With a low threshold, it is possible to decrease the error. For $TIR$ = 12 dB, the average error on all the sub-classes is 0.22 ($\pm$ 0.08) dB with $t$ = 0.30. In opposite for $TIR$ = -12 dB, it is better to choose a high threshold $t$ = 0.55, the error decrease then to 4.46 $\pm$ 1.66. In order to generalize this method where no prior knowledge on the urban environment, the chosen threshold $t$ is then fixed to $t$ = 0.42 and is the one that best balanced these opposite cases.
